---
title: "Sentiment Analysis of Twitter Data"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: readable
    social: menu
    navbar:
     - { title: "", 
         href: "https://alecrsf.netlify.app/en/", 
          icon: "fa-home"}
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```

# Basics {data-navmenu="Introduction"}

## 1Pane {sidebar}

### Intro

#### Vector data

The **vector data model** represents the world using points, lines and polygons. These have discrete, well-defined borders, meaning that vector datasets usually have a high level of precision.

The geographic vector data model is based on points located within a *coordinate reference system* (**CRS**)

##### Simple features

Simple features is an open standard developed and endorsed by the Open Geospatial Consortium (OGC)

##### Geometry types

Simple features in R can take on one of the 18 geometry types supported by the sf package. In this chapter we will focus on the seven most commonly used types: POINT, LINESTRING, POLYGON, MULTIPOINT, MULTILINESTRING, MULTIPOLYGON and GEOMETRYCOLLECTION. Find the whole list of possible feature types in the PostGIS manual.

<br>

#### Raster data

The **raster data model** divides the surface up into cells of constant size. Rasters aggregate spatially specific features to a given resolution, meaning that they are consistent over space and scalable. The raster data model usually consists of a raster header and a matrix (with rows and columns) representing equally spaced cells.

### Data

```{r, echo=FALSE, warning=FALSE}
tibble::tribble(
  ~`Package`, ~Description,
  "osmdata", "Download and import small OpenStreetMap datasets.",
  "osmextract", "Download and import large OpenStreetMap datasets.",
  "geodata", "Download and import imports administrative, elevation, WorldClim data.",
  "rnaturalearth", "Access to Natural Earth vector and raster data.",
  "rnoaa", "Imports National Oceanic and Atmospheric Administration (NOAA) climate data."
) %>% 
knitr::kable(caption = "Selected R packages for geographic data retrieval.", 
             caption.short = "Selected R packages for geographic data retrieval.",
             booktabs = TRUE) %>% 
  kableExtra::kable_styling(latex_options="scale_down")
```

<https://code.highcharts.com/mapdata/>

# Highcharter {data-navmenu="Packages"}

## Column

### Highcharter

#### Highcharter

```{r}
library(highcharter)
```

<https://code.highcharts.com/mapdata/>

-   `download_map_data()`: Download the geojson data from the highchartsJS collection.
-   `get_data_from_map()`: Get the properties for each region in the map, as the keys from the map data.

# Leaflet {data-navmenu="Packages"}

## Column

### Leaflet

#### Leaflet

```{r}
library(leaflet)
```

For working with *GeoJSON/TopoJSON* data you have two options: either read it into *sp* objects; or use the `addGeoJSON()` and `addTopoJSON()` functions
