---
title: "Sentiment Analysis of Twitter Data"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    theme: readable
    social: menu
    navbar:
     - { title: "", 
         href: "https://alecrsf.netlify.app/en/", 
          icon: "fa-home"}
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
```

# Basics {data-navmenu="Introduction"}

## 1Pane

### Intro

#### Sentimental Analysis 

The **vector data model** represents the world using points, lines and polygons. These have discrete, well-defined borders, meaning that vector datasets usually have a high level of precision.

The geographic vector data model is based on points located within a *coordinate reference system* (**CRS**)

# Highcharter {data-navmenu="Packages"}

## Column

### Highcharter

#### Highcharter

```{r}
library(highcharter)
```

<https://code.highcharts.com/mapdata/>

-   `download_map_data()`: Download the geojson data from the highchartsJS collection.
-   `get_data_from_map()`: Get the properties for each region in the map, as the keys from the map data.

# Leaflet {data-navmenu="Packages"}

## Column

### Leaflet

#### Leaflet

```{r}
library(leaflet)
```

For working with *GeoJSON/TopoJSON* data you have two options: either read it into *sp* objects; or use the `addGeoJSON()` and `addTopoJSON()` functions
